---
title: "Developing Data Products - Shiny App Pitch"
author: "DataSharer07"
date: "November 22, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Fantasy Football has gained Popularity

```{r,echo=FALSE,message=FALSE}
library(plotly)
library(ggplot2)
trend<-data.frame(year=c(2005:2011,2014:2016),players=c(12.6,18.0,19.4,29.9,28.4,32.0,35.9,41.5,56.8,57.4))
p<-ggplot(trend, aes(x = year, y = players)) + geom_line()+geom_point(size=2)+labs(x="Year",y="Estimated Players in Million")+ggtitle("Estimated number of fantasy sports players in USA & Canada by year")+ annotate("text", label = "Data from http://fsta.org/research/industry-demographics/ (Nov, 2016)", x = 2010, y = 10, size = 4, colour = "black")
(gg<-ggplotly(p))
```

## Most Important Fantasy Selection: QB!!!

I want to help you research and select your potential fantasy QB selection.
The data used in this project includes QB performance from the 2016 season and was retrieved from [here](https://nathanbrixius.wordpress.com/category/fantasy-football/).

The app allows you to explore different QB measures. The measures that you selected are illustrated in a table that displays the top QBs and an interactive plot.

## Adjust Fantasy Points based on your League Setup

Every league has the opportunity to customize the scoring of each player.With my app you can adjust 

- Passing TD Score
- Passing Yards Score
- Rushing TD Score
- Rushing Yards Score
- Lost Fumble Score
- Interception Score

Note: 2-pt converisons were not included in the data.

## Did you find your Fantasy QB?

If you did not, the app can be found [here](https://datasharer07.shinyapps.io/fantasyqb2016/).

Now, go win your league(s)!!!